Manuscript

### 2016-02-14 inst/wtc-finland/manuscript.Rmd
Change package name

```{r initialize}
library(parallel)
library(doMC)
registerDoMC(cores=detectCores())
library(WTC)
source("~/git/Winter-Track-Counts/setup/WTC-Boot.R")
library(sp)
library(ggplot2)
library(rasterVis)
library(reshape2)
library(plyr)

>>>>

```{r initialize}
library(parallel)
library(doMC)
registerDoMC(cores=detectCores())
library(STREM)
source("~/git/STREM/setup/WTC-Boot.R")
library(sp)
library(ggplot2)
library(rasterVis)
library(reshape2)
library(plyr)

### 2016-02-14 inst/wtc-finland/manuscript2.Rmd
Change package name

```{r initialize}
#library(devtools)
#install_github("statguy/WTC")
#install_github("ropengov/gisfin")
#install_github("statguy/Blur")
library(parallel)
library(doMC)
registerDoMC(cores=detectCores())
library(WTC)
source("~/git/Winter-Track-Counts/setup/WTC-Boot.R")
library(ggplot2)
library(scales)
library(grid)
library(plyr)
library(gridExtra)
library(Blur)

@@

>>>>

```{r initialize}
#library(devtools)
#install_github("statguy/STREM")
#install_github("ropengov/gisfin")
#install_github("statguy/Blur")
library(parallel)
library(doMC)
registerDoMC(cores=detectCores())
library(STREM)
source("~/git/STREM/setup/WTC-Boot.R")
library(ggplot2)
library(scales)
library(grid)
library(plyr)
library(gridExtra)
library(Blur)

@@

```{r table-1}
writeTable <- function(df, filename, context) {
  library(ReporteRs)
  doc <- docx()
  flextable <- FlexTable(df)
  addFlexTable(doc, flextable)
  dir <- normalizePath(context$figuresDirectory)
  writeDoc(doc, file=file.path(dir, filename))
}

models <- data.frame(Species=c("Canis Lupus"), Model=c("Intercept-only"), WAIC=c("1074.72"))
models <- rbind(models, data.frame(Species=c("Canis Lupus", "Canis Lupus"), Model=c("All PCs", "PC1 habitat 250 + PC2 all 64000"), WAIC=c("1074.78", "1072.57")))
models <- rbind(models, data.frame(Species=c("Canis Lupus", "Canis Lupus"), Model=c("All non-PCs 32000", "All non-PCs 16000"), WAIC=c("1061.45", "1067.00")))
models <- rbind(models, data.frame(Species=c("Lynx Lynx"), Model=c("Intercept-only"), WAIC=c("3922.51")))
models <- rbind(models, data.frame(Species=c("Lynx Lynx", "Lynx Lynx"), Model=c("All PCs", "PC3 all 8000"), WAIC=c("3930.95", "3914.81")))
models <- rbind(models, data.frame(Species=c("Lynx Lynx", "Lynx Lynx"), Model=c("All non-PCs 2000", "All non-PCs 8000"), WAIC=c("3917.34", "3917.35")))
writeTable(models, "table-b-1.docx", context)
```
